%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Master's Degree in Computer Science} % Degree
    {University of Cagliari, Faculty of Sciences, Department of Mathematics and Computer Science} % Institution
    {Cagliari, Italy} % Location
    {Sep. 2012 - Sep. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Cryptography.}
		\item {Biometrics and security.}
		\item {Embedded systems, kernel modules and device drivers development on Linux.}
		\item {Virtualization on Linux through \textit{kvm}, \textit{Eucalyptus} and \textit{OpenNebula}.}
		\item {Mobile Android applications development.}
		\item {Data Mining, Knowledge Discovery, clustering and classification algorithms.}
		\item {\textit{noSQL} database.}
		\item {Polygonal triangulation and orthogonal research algorithms implementation through \textit{C++} and \textit{Qt} libraries.}
		\item {Elaboration and analysis of digital images.}
		\item {Mathematical optimization and \textit{TSP}-like problems resolution through \textit{OPL}.}
		\\
		\\
		Thesis: "\textit{Predicting website content semantics from the interface appearance}" \downlink{https://drive.google.com/file/d/1GL2UrddCBHOzB_r4lnO4QYE3SDgJ95hk/edit}
		\\
		\\
		Mark: \textit{109/110}.
      \end{cvitems}
    }
    
    %-------------------------------------------------------
    
    \cventry
    {Bachelor's Degree in Computer Science} % Degree
    {} % Institution
    {} % Location
    {Oct. 2008 - Dec. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {C language programming.}
		\item {Algorithms and data structure, complexity analysis.}
		\item {Object-oriented programming and \textit{Java}.}
		\item {Functional programming and \textit{OCaml} language.}
		\item {Automates and formal languages, programming languages theory.}
		\item {Software engineering, \textit{UML}.}
		\item {Operating systems, multi-thread processing applications on Linux.}
		\item {Computer architectures, \textit{ASM} programming.}
		\item {Databases, \textit{MySQL}.}
		\item {Human-computer interaction.}
		\item {Probability and statistics.}
		\item {Economy and social rights.}
		\\
		\\		
		Mark: \textit{99/110}.
      \end{cvitems}
    }
    
    %-------------------------------------------------------
    
    \cventry
    {High School Diploma, Scientific studies} % Degree
    {Istituto Comprensivo Globale "\textit{Filiberto Farci}", Liceo Scientifico "\textit{F.lli Bissiri}"} % Institution
    {Via S. Giorgio 230, 08037 Seui, OG, Italy} % Location
    {Sep. 2000 - Jun. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points        	
		Mark: \textit{87/100}.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
