%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------------------
    \cventryextendedwithdoubletags
    	{Software Engineer II, Backend} % Job title
    	{Moneyfarm Ltd.} % Organization
    	{Viale Trieste, 163, 09123 Cagliari, CA} % Location
    	{Mar 2022 - CURRENT} % Date(s)
    	{
    	\begin{cvitem}
    	My team main focus is on external partner relationship, to whom we provide our platform as a service.
            The working group includes several back-end engineers, a QA, a PO and few front-enders. Main technology keys:
            \begin{itemize}
                \item Micro-services architecture (\textit{Terraform} and \textit{Kubernetes})
                \item Scala \textit{2.13} on \textit{JDK 11}, with \textit{Akka} and \textit{Cats}
                \item MySQL 8
                \item CI/CD with \textit{GitLab}
                \item Monitoring powered by \textit{Kibana} and \textit{Graphana}
            \end{itemize}
            Our architecture consists of a hundred services, that communicates both synchronously through API call and events as we are working for migrating it to an event-driven structure (through \textit{Kafka}).
    	My team follows a hybrid \textit{Kanban/Scrum} approach, giving us the flexibility to extreme release (hundred times per         week). Main activities:
    	\begin{itemize}
    	    \item Analysis, design and implementation of new product functionalities;
    	    \item Public APIs, Event and Architecture guilds
                \item Complexity estimation;
                \item REST API/Event develop and extension;
      	    \item Database design and implementation.
    	\end{itemize}
            Given my team focus and the lack of domain segregation in our architecture, the day-by-day work might include several different domains. Depending on the kind of initiative, I might have to extend the user activation flow, or the invoice generation process. We work like cross-domain, and I have to be flexible and know as much as possible of the entire platform.
    	\end{cvitem}
    	}
    	{
    	}
        {Scala, Akka, Java, Docker, MySQL, Kafka, GitLab, AWS}
        {Micro-services, FinTech}

%---------------------------------------------------------------------
    \cventryextendedwithdoubletags
    	{Team Lead, Consultant, Software Developer Specialist} % Job title
    	{Accenture Technology S.r.l.} % Organization
    	{Piazzetta L'Unione Sarda, 24, 09122, Cagliari, CA} % Location
    	{Sep 2021 - Feb 2022} % Date(s)
    	{
    	\begin{cvitem}
    	I worked on \textit{Healthcare and Public Service} Business Unit, involved on some projects for the \textit{Regione Autonoma della Sardegna} client. Main activities:
    	\begin{itemize}
    	    \item Analysis, design and implementation of new product functionalities;
            \item Time and complexity estimation;
            \item REST API develop and extension;
      	    \item Database interaction.
    	\end{itemize}
    	\end{cvitem} 
    	}
    	{
    	\begin{cvitems}
    	  \item {\textit{\textbf{SIBAR-SB}}: an automated information system for the management of protocol and document flows, which is the base of the work of all the offices. The core of this system is a micro-services architecture, based on \textit{Spring}. Those micro-services interact with various databases (\textit{OracleDB}, \textit{MongoDB}, \textit{mySQL}) and also includes various client built on \textit{Angular}. This architecture is deployed on \textit{Kubernetes}.
    	  The project is driven by a kind of \textit{Scrum-ban} approach (\textit{Jira}), and we ensure \textit{Continuous Integration} and \textit{Deployment}, through \textit{GitLab}.
      	}
    	\end{cvitems}
    	}
        {Java, Spring, Spring Boot, Docker, MongoDB, GitLab}
        {Micro-services, Public Service}

%---------------------------------------------------------------------
    \cventryextendedwithdoubletags
    	{Software Engineer, Research and Innovation} % Job title
    	{Inpeco TPM S.r.l.} % Organization
    	{Parco Scientifico e Tecnologico, Edificio 8, 09010 Pula, CA, Italy} % Location
    	{Nov 2019 - Aug 2021} % Date(s)
    	{
    	\begin{cvitem}
    	I took part in two of the main company's project, focused on laboratory automation on healthcare: \textit{TPM} and \textit{ProTube Suite}. Main activity has been:
    	\begin{itemize}
    	    \item Analysis, design and implementation of new product functionalities;
            \item Time and complexity estimation;
            \item Unit, Integration and Contract testing;
            \item Study new technologies and evaluate their introduction into projects.
    	\end{itemize}
    	We based our job on the \textit{Scrum Nexus} framework, and I was part of the Scrum team as \textit{back-end developer specialist}.
    	\end{cvitem} 
    	}
    	{
    	\begin{cvitems}
    	  \item {\textit{\textbf{TPM}}: a cloud based R\&D project, with the aim of patient healthcare data handling. Its core is composed by a bucket of public API, served by a micro-services architecture hosted on Kubernetes. I worked on \textit{Java Spring} based micro-services:
    	    \begin{itemize}
      	    \item REST API develop and extension;
      	    \item Spring Security (JWT and OAuth2);
      	    \item Database interaction (PostgreSQL, Azure Tables).
  	        \end{itemize}
  	        I also implemented authentication modules for \textbf{TS-CNS} and \textbf{SPID} (\textit{Python} micros-services based on \textit{Django}). The project has \textit{Continuous Integration} and \textit{Deployment} (with \textit{Unit}, \textit{Integration}, \textit{Contract} testing and artefacts creation).
      	}
    	  \item {\textbf{\textit{ProTube Suite}}: a pool of devices and services that fully automates the sample collection in the hospital. In particular, I worked on the back-end core framework (Java), and their interaction with the client applications (Android...). I worked both on new functionalities and bug fixing.
    	  }
    	\end{cvitems}
    	}
        {Java, Spring, Spring Boot, Docker, Jenkins, Azure}
        {Micro-services, Scrum, Healthcare}
        
%---------------------------------------------------------
        \cventrywithdoubletags
	    {Senior Analyst, Software Engineering} % Job title
    	{Avanade Italy} % Organization
    	{Piazza L’Unione Sarda, 26, 09122 Cagliari, Italy} % Location
    	{Jun 2018 - Oct 2019} % Date(s)s
    	{
      	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {\textit{Carrefour Italia}: I led a small team that was focused on Application Maintenance of a various customer's systems:
      		\begin{itemize}
  				\item Public and Internal Android/iOS Apps, based on \textit{Ionic Serve} Framework
  				\item Internal Intranet, based on Microsoft Sharepoint 2013
			\end{itemize}
			}
      	\item {\textit{Ministero degli Affari Esteri e della Cooperazione Internazionale}: I led a small team (3 people), during the developing of a Public Web Portal, based on ASP.Net MVC 5 framework. This web-site architecture has been based on DB first approach, using both Entity and Identity Framework. }
            \item {\textit{Sorgenia S.p.A.}: I have continuously improved my Technical Leading skills, including studying and achieving Scrum and Agile techniques focused certifications. I have also participated in some external System Integration activities. I have been more involved on functional decision and designing support.}
            \item {Taking part in on-call rotation (night-time and holidays) for production systems.}
    	\item {I have been involved on internal company activities, such as Interviews for Internships and Internal Hands-On focus groups.}
      	\end{cvitems}
        }
        {ASP.Net MVC 5, C\#, SQL Server, Android, iOS, Azure}
        {Retail, Public Service, Team Leading, Business \& Integration, App. Dev.}
    
	\cventrywithdoubletags
    	{Analyst II-III, Software Engineer} % Job title
    	{} % Organization
    	{} % Location
    	{Jun 2016 - May 2018} % Date(s)    	
    	{
      	\begin{cvitems} % Description(s) of tasks/responsibilities
        	\item {\textit{Sorgenia S.p.A.}: Led teams in CRM and Digital project streams, including disaster recovery activities and external system integration. My team also involved off-shore colleagues (\textit{India Delivery}). Worked on sales management, ERP, and credit management.}
        	\item {\textit{McDonald's Italia}: software maintenance and small change requests with direct interaction with the stakeholders.}
        	\item{I have got involved on internal company activities, like technical hiring talks with junior candidates.}
      	\end{cvitems}
        }
        {X++, SQL Server, TFS, MS Dynamics, Mecoms, Azure}
        {ERP, Energy \& Utilities, Integration, App. Dev.}
        \cventrywithdoubletags
    	{Analyst I, Software Engineer} % Job title
    	{} % Organization
    	{} % Location
    	{Apr. 2015 - May 2016} % Date(s)
    	{
      	\begin{cvitems} % Description(s) of tasks/responsibilities
       \item{Main  client companies: \textit{Sorgenia S.p.A} (Energy) and {\textit{McDonald's Italy} }(Food).
        Handled software maintenance and small change requests on their internal ERP systems. Served near shore for both projects.}
      	\end{cvitems}
        }
        {X++, SQL Server, TFS, MS Dynamics AX, Mecoms}
        {ERP, Energy \& Utilities, Retail, App. Dev.}

%---------------------------------------------------------------------
    \cventrywithtags
    	{Intern, Programmer Solution Factory} % Job title
    	{Avanade Italy} % Organization
    	{Via Lepetit, 8/10, 20124 Milano, Italy} % Location
    	{Oct. 2014 - Apr. 2015} % Date(s)
    	{
      	\begin{cvitems} % Description(s) of tasks/responsibilities
        	\item {\textit{Avanade Academy}: 6 weeks of training on Microsoft Technologies and Tools (like \textit{C\#}, \textit{ASP.Net}, \textit{MVC 5}, \textit{Visual Studio 2012}, \textit{Team Foundation Server}) and Web Based Technologies (\textit{JavaScript}, \textit{AJAX}, \textit{HTML5}, \textit{CSS}).}
        	\item {\textit{Manutencoop Facility Management S.p.A. }: software maintenance and small change requests on dedicated Intranet back-end, based on \textit{Microsoft SharePoint 2013} (1 month).}
        	\item {\textit{Sorgenia S.p.A.}: first contact with the \textit{Microsoft Dynamics AX 2012 R3} and \textit{MECOMS} platforms (aimed to Utilities market). On the first period, I have been engaged on trainings and small tasks assignments. On the second period I worked on whole SDDs, focused on Sales management (Contracts, Customer Data, Global Address Book). I also collaborated with near shore consultants (working for \textit{Ferranti Computer Systems}), in order to improve my expertise on \textit{MECOMS} platform. On site working.
        }
      	\end{cvitems}
        }
        {C\#, ASP.Net, JavaScript, HTML5, CSS, TFS, VS}
    
%---------------------------------------------------------------------
    \cventrywithdoubletags
    	{Undergraduate Teaching Assistant} % Job title
    	{Università degli Studi Cagliari} % Organization
    	{P. delle Scienze, Via Ospedale, 72, 09124 Cagliari, Italy} % Location
    	{Mar. 2013 - Jun. 2014} % Date(s)
    	{
      	\begin{cvitems} % Description(s) of tasks/responsibilities
        	\item {Teaching assistant for the course \textit{Amministrazione di Sistema (System Administration) [INF/01]} part of the \textit{Bachelor's Degree on Computer Science} curricola. Main subjects of the course: web development basics, internet applications, \textit{HTTP} protocol, client and server side architecture/development. I have served as Assistant twice.}        	
      	\end{cvitems}
        }
        {HTTP, Web Applications}
        {Tutoring}
    
%---------------------------------------------------------------------
    \cventrywithdoubletags
    	{Graduate Intern} % Job title
    	{Regione Autonoma della Sardegna} % Organization
    	{Via Roma, 223, 09123 Cagliari, Italy} % Location
    	{Mar. 2012 - Aug. 2012} % Date(s)
    	{
      	\begin{cvitems} % Description(s) of tasks/responsibilities
        	\item {Collaborating with the office \textit{Direzione Generale della Sanità, "Servizio sistema informativo, osservatorio epidemiologico umano, controllo di qualità e gestione del rischio"} (\textit{Regional Healthcare System}), I have served as data analyst focused on healthcare information knowledge.}
      \end{cvitems}
        }
        {Java, SQL, Databases}
        {Data Analysis, Healthcare, Public Service}
    
    %---
    
    \cventrywithdoubletags
    	{Undergraduate Intern} % Job title
    	{} % Organization
    	{} % Location
    	{Apr. 2011 - Sept. 2011} % Date(s)
    	{
      	\begin{cvitems} % Description(s) of tasks/responsibilities
        	\item {Part of the \textit{Bachelor's Degree} on-the-job training. I have achieved knowledge on healthcare information systems, developing a solution that handles a specific data flow. Skills achieved/improved: \textit{SQl Server Mangement Studio}, \textit{Microsoft Access}, \textit{Java}.}
      	\end{cvitems}
        }
        {Java, SQL, Databases}
        {Data Analysis, Healthcare, Public Service}

\end{cventries}